An R Markdown document converted from "03_ValClusOutcomes.ipynb

### 2023-07-31 03_ValClusOutcomes.Rmd
Add files via upload

If any of the columns in this table are missing in your data, one option is to assume that none in your population had the disease.

@@

<!-- BIBLIOGRAPHY START -->
<div class="csl-bib-body">
  <div class="csl-entry"><i id="zotero|10831815/UYLBIXH3"></i>
    <div class="csl-left-margin">1. </div><div class="csl-right-inline">Coenders G, Pawlowsky-Glahn V. On interpretations of tests and effect sizes in regression models with a compositional predictor. SORT-Statistics and Operations Research Transactions [Internet]. 2020 Jun 26 [cited 2023 Jul 28];44(1):201–20. Available from: https://raco.cat/index.php/SORT/article/view/371189</div>
  </div>
  <div class="csl-entry"><i id="zotero|10831815/ZY2CL5NC"></i>
    <div class="csl-left-margin">2. </div><div class="csl-right-inline">SCORE2 working group and ESC Cardiovascular risk collaboration. SCORE2 risk prediction algorithms: new models to estimate 10-year risk of cardiovascular disease in Europe. European Heart Journal [Internet]. 2021 Jul 1 [cited 2023 Jul 20];42(25):2439–54. Available from: https://doi.org/10.1093/eurheartj/ehab309</div>
  </div>
  <div class="csl-entry"><i id="zotero|10831815/FPUFQKFI"></i>
    <div class="csl-left-margin">3. </div><div class="csl-right-inline">SCORE2-Diabetes Working Group and the ESC Cardiovascular Risk Collaboration. SCORE2-Diabetes: 10-year cardiovascular risk estimation in type 2 diabetes in Europe. European Heart Journal [Internet]. 2023 May 29 [cited 2023 Jul 13];ehad260. Available from: https://doi.org/10.1093/eurheartj/ehad260</div>
  </div>
</div>
<!-- BIBLIOGRAPHY END -->

>>>>

If any of the columns in this table are missing in your data, one option is to assume that none in your population had the disease, i.e., you should have a column with all 0.

@@

<!-- BIBLIOGRAPHY START -->
<div class="csl-bib-body">
</div>
<!-- BIBLIOGRAPHY END -->
